A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-04-06 2022/Sensors/sensors.tex
add one more figure and comment

@@

>>>>

We employed in our experiments the kNN-KD method from the scikit-learn library; this method was used with default settings. For our kNN-ME method, we used the evolvent density $m=12$, the number of evolvents simultaneously used was $L=10$ for datasets 1 -- 3 and $L=7$ for the last dataset.

@@

The time required to find K nearest neighbours on the CarEvoluation dataset is shown in Fig.~\ref{fig6a}. In this experiment, the number of evolvents used simultaneously was 7. 
\begin{figure}
\widefigure
\includegraphics[width=0.5\linewidth]{fig6a.png}
\caption{Comparison of neighbour search times for the CarEvoluation dataset\label{fig6a}}
\end{figure}
The results of the comparison on this dataset also demonstrate that the kNN-ME method is faster compared to the kNN-KD method.
